Verified Time Balancing of Security Protocols

### 2019-01-20 Src/talk.tex
Finished Talk, need to practice

\begin{frame}[fragile]
  \frametitle{Motivation}
  \begin{itemize}
    \item ASD manually verifies vendor code with containing cryptographic
            processes.
    \item Formal Methods: A mathematically based approach to the
            specification and verification of software.
    \item Can we reduce some of the resources ASD spends on 
            manual verification by replacing with automatic verification?
    \item A case study.
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Quick Background 2 - Propositions as Types}
     \begin{table}[h!]
    \begin{tabular}{c|c|c|c}
    \textbf{Logic Term} & \textbf{Logic Symbol} & \textbf{Idris Symbol}
      & \textbf{Idris Type} \\
    \hline
      Implication & p $\Rightarrow$ q & p \mintinline{haskell}{->} q
      & Arrow \\
      Conjunction & p $\land$ q & \mintinline{haskell}{(p, q)} 
      & Pair (Product) \\
      Disjunction & p $\lor$ q & \mintinline{haskell}{Either p q}
      & Enum (Sum)\\
      Negation & $\lnot$ p & \mintinline{haskell}{p -> Void} &
      Void Type \\
      IFF/Eq & p $\equiv$ q, p $\iff$ q & \mintinline{haskell}{(p -> q, q -> p)} 
      & Pair Arrows \\
      Universal & $\forall$ x. P x & 
      \mintinline{haskell}{p -> Type} & $\Pi$ Type \\
      Existential & $\exists$ x. P x 
      & \mintinline{haskell}{(x ** P x)} & $\Sigma$ Type \\
      \hline
       & & \mintinline{haskell}{p = q} & Type Equality
    \end{tabular}
  \end{table}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Capturing time invariants in a small DSL}
  %code for prg goes here, correct by construction
  \begin{minted}
  \end{minted}
\end{frame}

\begin{frame}[fragile]
  \frametitle{What about more expressive time parameters?}
  %discuss how in the case of mod, we can have the time parameter
  %expressed as a function of the input
\end{frame}

\begin{frame}[fragile]
  \frametitle{Elaboration and Compilation of a small correct core}
  %diagram on how a small correct core can be both elaborated and compiled
  %for compiled can be mapped to a specific chipset achitecture
\end{frame}

>>>>

\begin{frame}[fragile]
  \frametitle{Motivation}
  \begin{itemize}
    \item ASD manually verifies vendor code with containing 
          cryptographic processes.
    \item Formal Methods: A mathematically based approach to the
            specification and verification of software.
    \item Can we reduce some of the resources ASD spends on 
            manual verification by replacing with automatic 
            verification?
    \item A case study, also work towards more secure protocols.
  \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Quick Background 2 - Propositions as Types}
     \begin{table}[h!]
    \begin{tabular}{c|c|c|c}
    \textbf{Logic Term} & \textbf{Logic Symbol} & 
    \textbf{Idris Symbol} & \textbf{Idris Type} \\
    \hline
      Implication & p $\Rightarrow$ q & p \mintinline{haskell}{->} q
      & Function \\
      Conjunction & p $\land$ q & \mintinline{haskell}{(p, q)} 
      & Pair / Tuple \\
      Disjunction & p $\lor$ q & \mintinline{haskell}{Either p q}
      & Tagged Union\\
      Negation & $\lnot$ p & \mintinline{haskell}{p -> Void} &
      Void Type \\
      IFF/Eq & p $\equiv$ q, p $\iff$ q & 
        \mintinline{haskell}{(p -> q, q -> p)} 
      & Pair Arrows \\
      Universal & $\forall$ x. P x & 
      \mintinline{haskell}{p -> Type} & $\Pi$ Type \\
      Existential & $\exists$ x. P x 
      & \mintinline{haskell}{(x ** P x)} & $\Sigma$ Type \\
      \hline
       & & \mintinline{haskell}{p = q} & Type Equality
    \end{tabular}
  \end{table}
\end{frame}

@@

\begin{frame}[fragile]
  \frametitle{Building a type of Prg n}
  \begin{table}[h!]
  \begin{tabular}{c|c|c|c}
  Statement & Continuation & Result & Description \\
  \hline 
  Halt & Prg 1 & Prg 1 & Terminate \\
  AssC & Prg k & Prg (k + 1) & Asn constant. \\
  AssV & Prg k & Prg (k + 1) & Asn variable. \\
  UnOp & Prg k & Prg (k + 1) & Asn result of unary op. \\
  BinOP & Prg k & Prg (k + 1) & Asn result of binary op. \\
  Do & Prg k & Prg (m * n + k) & Run Prg m, n times. \\
  Cond & Prg k & Prg (n + k) & Branch on Prg n. \\
  \end{tabular} 
  \end{table}
  Conditionals require both branches to be Prg n. Ensuring
  That all branches of the program are correct by construction.
\end{frame}

\begin{frame}[fragile]
  \frametitle{What about more expressive time parameters?}
  \begin{minted}{haskell}
  f : Value -> Value -> Nat
  f = --some complex function to calculate the number of
      --computation steps for each input to mod.

  data Prg : Nat -> Type where
    Mod : {k : Nat} -> (cont : Prg k) -> (x : Value) ->
          (y : Value) -> Prg ((f x y) + k)
  \end{minted}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Elaboration and Compilation of a Correct Core}
  %diagram on how a small correct core can be both elaborated and 
  %compiled
  %for compiled can be mapped to a specific chipset achitecture
  \begin{minipage}[c]{5cm}
  \begin{center}
    \begin{tikzpicture}
      \node[shape=rectangle, draw=black, minimum size = 2cm] (Elab) 
           {Elaborator} ;
      \node[shape=rectangle, draw=black, minimum size = 2cm] (Prg) 
           [below = 1cm of Elab] {Correct Core};
      \node[shape=rectangle, draw=black, minimum size = 2cm] (Comp) 
           [below = 1cm of Prg] {Compiler};

      \path [->] (Prg) edge node {} (Elab);
      \path [->] (Prg) edge node {} (Comp);
  \end{tikzpicture}
  \end{center}
  \end{minipage}
  \begin{minipage}[c]{\textwidth-6cm}
  \begin{itemize}
    \item The small, correct core language can be elaborated to
          a more full-featured language.
    \item The size of the core language makes the burden of proofs
          much lighter.
    \item The compiler can map the core language expressions down
          to something more real world (e.g C, assembler).
  \end{itemize}
  \end{minipage}
\end{frame}
